---
title: 'CIND 123 - Assignment #4'
output:
  word_document: default
  pdf_document: default
---

This assignment makes use of pakcage "RCurl", accordingly carry out the following:
```{r load_packages}
#install.packages("RCurl")
library(RCurl) 
```
First we read the computers.csv file and load the price using the following: 
```{r}
u <- getURL("http://vincentarelbundock.github.io/Rdatasets/csv/Ecdat/Computers.csv")
cprices <- read.csv(text =u)
```
1) Display the first 6 rows of cprices and make note of all the variables.
```{r}
head(cprices,6)

```
2) Calculate the mean, variance and standard deviation of price by omitting the missing values, if any.
```{r}
sum(is.na(cprices$price))#"there are no missing values so na.omit command is not used"
price<-c(mean(cprices$price),var(cprices$price),sd(cprices$price))
names(price)<-c("Mean","Variance","StdDev")
price

```
3) Use `ram` to predict price and build a univariate linear regression model, display a summary of your model indicating Residuals, Coefficients..etc.
```{r}
priceonram<-summary(lm(price~ram,data = cprices))
priceonram

```
4) Based on the output of your model, predicted the expected price when ram is set to 8 MB
```{r}
predicted_price<-1687.29+64.23*8
predicted_price

```
5) Find Pearson correlation between hard disk and speed.
```{r}
correlation<-cor.test(cprices$hd,cprices$speed,method = "pearson")
correlation

```
6) Write the correlation matrix of the variables: price, speed, hd and ram.
```{r}
cor(cprices[,2:5])

```
7) Visualize the correlation of the numeric columns in the computer prices dataset.
```{r}
library(corrplot)
new_df_cprices<-cprices[,-(7:9)]
new_df_cprices
m<-cor(new_df_cprices)
corrplot(m,method = "ellipse")


```

END of Assignment #4.



