---
 R codes for normal distribution, binomial distribution and poisson distribution
---

This assignment questions make use of data that is provided by the
`ISwR` package.

```{r}
library(ISwR)
```

## Question 1 

In this question you will explore the airquality dataset available in the datasets library in the ISwR package.

a) Display the first 6 rows of the airquality dataset.

```{r}
head(airquality,6)

```

b) Display the type of each column of the airquality dataset, use only one function in R to do so.

```{r}
str(airquality)


```

c) Use a histogram to assess the normality of the `Ozone` variable.(In order to get the output diagram inserted in your answer use attach(dataframe name)) 
```{r}
attach(hist(airquality$Ozone))

```
d) Does it appear normally distributed? 
```{r}
#"The distribution does not look to be normal as the majority of observations are concentrated on the left side of the histogram figure "
```
e) Create a boxplot which shows the distribution of `Ozone` in each month.Use different colors for each month.
```{r}
boxplot(Ozone~Month,data=airquality,main="Different boxplots for each month",
  xlab= "Months", ylab="ozone", col= c("red","orange","blue","green","yellow"))

```
f) Create one scatter plot matrix of the numeric variable (Ozone, Solar.R,Wind,Temp) within the airquality dataset.
(Hint investigate pairs())

```{r}
pairs(airquality[,1:4])

```

## Question 2 
a)Use simulation to estimate the mean and variance of a binomial random variable with n = 18 and p = 0.76. 

```{r}
BinomialRV<-c(mean(rbinom(10000,18,.76)),var(rbinom(10000,18,.76)))
names(BinomialRV)<-c("Mean","Variance")
BinomialRV

```

b) Calculate the values using the theroy (state the value and the equation in your answer), compare the values you get with the values you got in (a), write one sentence summerizing the comparison.

```{r}
#"1. Mean of the binomial distribution is given by n*p, which is 13.68( calculated as 18*.76) and the variance is given by n*p*q, which is 3.2832(calculated as 18*.76*.24)" "2.the difference between the calculated values of mean and variance with 10000 simulation is almost similar to the theoretical values as calculated in (1) above" 

```

## Question 3  
a) Estimate the mean and variance of a Poisson random variable whose mean is 7.2 by simulating 10,000 Poisson random numbers.
```{r}
PoissonRV<-c(mean(rpois(10000,7.2)),var(rpois(10000,7.2)))
names(PoissonRV)<-c("Mean","Variance")
PoissonRV

```
b) Compare the mean value you got in (a), with the one stated in the question. Write one sentence summarizing the comparison.

```{r}
#
"The mean value of 10000 poisson random number as found in (a) above is almost similar to the one given in question. As we increase the number of simulation, the value of calculated mean approaches to the value of theoretical mean "
#
```
## Question 4  
Simulate 100 realizations of a normal random variable having a mean of 51 and a standard deviation of 5.2.
```{r}
NormalRV<-rnorm(100,mean=51,sd=5.2)
NormalRV

```

END of Assignment #3.



